---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bpscales

<!-- badges: start -->
[![R-CMD-check](https://github.com/context-dependent/bpscales/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/context-dependent/bpscales/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`bpscales` provides Blueprint-branded colour palettes for general applications and
scales for specific application to ggplot2 plots.



## Installation

You can install the development version of bpscales from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("context-dependent/bpscales")
```

## Palettes

The available palettes are categorized by two parameters: `type` and `option`.

```{r palettes}
library(bpscales)

show_blueprint_palettes()
```

## Discrete Data

> **Penguins:** The examples below use data from the [`palmerpenguins`](https://allisonhorst.github.io/palmerpenguins/)
> package, developed by Horst, Hill, and Gorman as an alternative to the `iris` dataset,
> which is [old, boring, and built by eugenicists](https://armchairecology.blog/iris-dataset/).

```{r discrete}
library(bpscales)
library(palmerpenguins)
library(ggplot2)
## basic example code

penguins |>
  ggplot(aes(bill_length_mm, flipper_length_mm)) +
  geom_point(aes(fill = species), shape = 21, size = 3) +
  scale_fill_blueprint(discrete = TRUE)

penguins |>
  ggplot(aes(bill_length_mm, flipper_length_mm)) +
  geom_point(aes(fill = species), shape = 21, size = 3) +
  scale_fill_blueprint(type = "linear", option = "green", discrete = TRUE)
```

## Continuous Data

```{r continuous}
penguins |>
  ggplot(aes(bill_length_mm, flipper_length_mm)) +
  facet_wrap(~species, nrow = 1) +
  geom_point(aes(fill = body_mass_g), shape = 21, size = 3) +
  scale_fill_blueprint(type = "multi", option = "fsc")
```